Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
remove bottom left text

%\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.

@@

Worse, operators can never be sure that their templates correctly implement the policy. %
Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which policies they implement and for which topologies---other than those of the configurations obtained from instantiating them.
%
Thus, operators validate templates by testing some concrete instantiations using
simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. This testing is insufficient because large networks evolve continuously as
devices and links are added or taken offline for maintenance. Templates that
work for the current topology, may or may not work for future
topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
may cause trickle-down, network-wide configuration changes, which is highly
disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

Given the challenges of generating and validating network configurations, one
might think that operators will be receptive to systems that can generate
provably-correct configurations from high-level policy
specifications~\cite{narain+:configassure,propane}. However, our conversations
with two major cloud providers reveal that operators of large networks are
reluctant to use such systems. While they think of their network abstractly, in
terms of roles, these systems only understand concrete topologies, with no understanding of roles.  Even if two devices play the same role,
there is no guarantee that the systems will generate (syntactically) similar
configurations; if the operators want to debug or analyze system output, they
will have to consider hundreds of device configurations instead of a handful of
role configurations. These systems become even more brittle when the network
evolves. Any change in network topology requires re-execution of the engine,
from scratch, on the new topology.  The result may be a completely different
set of configurations.

We present \sysname, a system to generate provably-correct role templates. It
allows operators to input \emph{abstract network topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). Other inputs to \sysname include the routing policy of the
network and its fault-tolerance requirements (e.g., the number of link failures
to tolerate). For high-level specification of routing policy, we borrow notation from
Propane~\cite{propane}. But while Propane policies refer to concrete devices, \sysname
policies refer to abstract roles.

>>>>

%\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
%\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.

@@

Worse, operators can never be sure that their templates correctly implement the policy. %
Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which policies they implement and for which topologies---other than those of the configurations obtained from instantiating them.
%
Thus, operators validate templates by testing some concrete instantiations using
simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. This testing is insufficient because large networks evolve continuously as
devices and links are added or taken offline for maintenance. Templates that
work for the current topology, may or may not work for future
topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
may cause trickle-down, network-wide configuration changes that are highly
disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

Given the challenges of generating and validating network configurations, one
might think that operators will be receptive to systems that can generate
provably-correct configurations from high-level policy
specifications~\cite{narain+:configassure,propane,synet-synthesis}. However, our conversations
with two major cloud providers reveal that operators of large networks are
reluctant to use such systems. While they think of their network abstractly, in
terms of roles, these systems only understand concrete topologies, with no understanding of roles.  Even if two devices play the same role,
there is no guarantee that the systems will generate (syntactically) similar
configurations; if the operators want to debug or analyze system output, they
will have to consider hundreds of device configurations instead of a handful of
role configurations. These systems become even more brittle when the network
evolves. Any change in network topology requires re-execution of the engine,
from scratch, on the new topology.  The result may be a completely different
set of configurations.

We present \sysname, a system to generate provably-correct role templates. It
allows operators to input \emph{abstract network topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). Other inputs to \sysname include the routing policy of the
network and its fault-tolerance requirements (e.g., the number of simultaneous link failures
to tolerate). For high-level specification of routing policy, we borrow notation from
Propane~\cite{propane}. But while Propane policies refer to concrete devices, \sysname
policies refer to abstract roles.
